music

### 2020-03-14 analysis/22_symphony.Rmd
moving to musical genes

turquoisegenes <- d4 %>%
  filter( modulecolor == "turquoise",
          tissue == "pituitary") %>%
  droplevels() %>% 
    ggplot(aes(x = treatment, y = m)) +
  geom_image(aes(image=image), size = 0.15) +
  geom_smooth(aes(x = as.numeric(treatment)), se = F, color = "turquoise") +
  facet_wrap(~modulecolor, scales = "free_y", nrow = 2) +
  labs(subtitle = "WGCNA turquoise module", 
       y = "gene expression  in the pitutiary", x = "parental stage") +
    facet_wrap(~gene, scales = "free_y", nrow = ) +
    theme_B3() +
    theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "italic"))

redgenes <- d4 %>%
  filter( modulecolor == "red",
          tissue == "pituitary") %>%
  droplevels() %>% 
    ggplot(aes(x = treatment, y = m)) +
  geom_image(aes(image=image), size = 0.15) +
  geom_smooth(aes(x = as.numeric(treatment)), se = F, color = "red") +
  facet_wrap(~modulecolor, scales = "free_y", nrow = 2) +
  labs(subtitle = "WGCNA red module", 
       y = "gene expression  in the pitutiary", x = "parental stage") +
    facet_wrap(~gene, scales = "free_y", nrow = ) +
    theme_B3() +
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "italic"))

turquoisegenes
redgenes

plot_grid(turquoisegenes, redgenes)
```

>>>>

redgenes <- d4 %>%
  filter( modulecolor == "red",
          tissue == "pituitary") %>%
  droplevels() %>% 
    ggplot(aes(x = treatment, y = m)) +
  geom_errorbar(aes(ymin=m-se, ymax=m+se, color=treatment), width=.1) +
  geom_image(aes(image=image), size = 0.15) +
  #geom_smooth(aes(x = as.numeric(treatment)), se = F, color = "red") +
  facet_wrap(~modulecolor, scales = "free_y", nrow = 2) +
  labs(subtitle = "WGCNA red module", 
       y = "gene expression  in the pitutiary", x = "parental stage") +
    facet_wrap(~gene, scales = "free_y", nrow = ) +
    theme_B3() +
    theme(legend.position = "none", 
          axis.text.x = element_text(angle = 45, hjust = 1),
          strip.text = element_text(face = "italic")) +
  scale_color_manual(values = allcolors)

redgenes
